\documentclass[11pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\setlength{\parindent}{0pt}
\setlength{\topsep}{0pt}
\setlist{nolistsep}
\pagenumbering{gobble}

\newcommand{\ressection}[1]{%
  \vspace{12pt}{\Large{\textsc{#1}}} \titlerule[0.5pt] \par
}

\begin{document}
\begin{samepage}
\begin{tabbing}
  \textbf{\LARGE{Joshua Towner}}\\
  \href{https://joshua.towner.xyz}{https://joshua.towner.xyz} \` 505 Congress St Unit 911, Boston, MA \\
  \href{mailto:josh@towner.xyz}{josh@towner.xyz} \` 781-361-9585
\end{tabbing}

\ressection{Education}
\begin{tabbing}
  \textbf{Northeastern University}, Boston, MA \` Sep 2017\,--\,May 2021 \\
  Bachelor of Science in Computer Science/Physics and Math \`  \textbf{GPA:} 3.96/4.00\\
  \textit{Relevant Courses}: \= Object Oriented Design \hspace{1em} \= Algorithms \hspace{4em} \= Machine Learning \\
  \>  Quantum Mechanics  \> Applied Analysis \> Optimization and Complexity \\ 
  \textit{Activities}: \> Society of Physics Students Webmaster \> \> Husky Competitve Programming Club
\end{tabbing}

\ressection{Computer Knowledge}
\begin{tabbing}
  \textbf{Languages}: \hspace{2.5em}\=
  \textit{Proficient}: \hspace{1.2em} \=Java, Python, SQL, JS, TS, HTML, CSS, React, \LaTeX \\
  \>\textit{Familiar with}: \>Go, C\#, C++, C, Mathematica, Bash, VB, Sass, Octave \\
  \textbf{Software/APIs}:\>
  \textit{Proficient}: \>Linux, Profiling, CI, Android, Git, Docker, NumPy, SciPy, AWS \\
  \>\textit{Familiar with}: \>GCP, Gitlab/Github/Circle CI, K8s
\end{tabbing}

\ressection{Work Experience}

\begin{tabbing}
  \textbf{AWS}, Boston, MA \` Jul 2021\,--\,Present \\
  Software Development Engineer II
\end{tabbing}
\begin{itemize}
  \item Architected, coordinated, developed, and deployed key features 
  of a new hybrid backup service, including data upload, 
  error reporting, and a proprietary incremental diff solution, 
  all at AWS Scale. 
  \item Improved team processes, including release and 
  security management. Led sessions regarding the service and onboarding. 
  Mentored new team members, including 
  an intern that completed their project on time.
\end{itemize}

\begin{tabbing}
  \textbf{Anna}, Remote \` Sep 2019\,--\,May 2021 \\
  Lead Software Engineer
\end{tabbing}
\begin{itemize}
  \item Architected and developed a smart vending machine system, including 
  real-time approvals of orders, pre-ordering, and serial communication 
  with the machine, including deployment onto AWS and scalability.
  \item Managed the entire engineering team, efficiently 
  planning out work and new features.
\end{itemize}

\begin{tabbing}
  \textbf{Intuit}, Boston, MA \` Jun 2020\,--\,Dec 2020 \\
  Software Engineering Co-op
\end{tabbing}
\begin{itemize}
  \item{Developed and released full stack features in the Quickbooks contractor payment system.
  This product already hosts 30,000+ contractors and has moved 60+ million dollars.}
\end{itemize}

\begin{tabbing}
  \textbf{Mercari}, Boston, MA \` Jul 2019\,--\,Dec 2019 \\
  Backend/ML Software Co-op
\end{tabbing}
\begin{itemize}
  \item Spearheaded redesign of Python and Java recommender systems reducing resource usage by 92\%, adding online capabilities, and improving recommendations serving 25 million users.
\end{itemize}

\begin{tabbing}
  \textbf{Northeastern University Venkatachalam Lab}, Boston, MA \` May 2019\,--\,Oct 2019 \\
  Undergraduate Research Assistant
\end{tabbing}
\begin{itemize}
  \item Utilized Python, specifically SciPy and Keras, to create and boost a nematode neuron detection model.
\end{itemize}

\begin{tabbing}
  \textbf{Harrow Search}, Boston, MA \` Oct 2018\,--\,Jun 2019 \\
  Software Developer
\end{tabbing}
\begin{itemize}
  \item Developed Selenium service to scrape websites and then store and analyze scraped data in Django.
\end{itemize}

\begin{tabbing}
  \textbf{Northeastern Khoury College}, Boston, MA \` Jan 2020\,--\,Present \\
  Algorithms TA
\end{tabbing}

\ressection{Interests}
\begin{center}
Video Games (any Paradox game, Elite) \textbullet\ Skiing \textbullet\ Charity Biking \textbullet\ The Office, Star Wars, Marvel \\
Machine Learning \textbullet\ Artificial Intelligence \textbullet\ Algorithms\ \textbullet\ Optimization \textbullet\ Quantum Computing
\end{center}
\end{samepage}

\end{document}
